---
title: "Bold, Centered, and Title Cased: Do Not Use All Caps for Your Title"
author-one: Amos O. Okutse
institution-one: Department of Biostatistics, School of Public Health, Brown University, 121 South Main Street, Providence, RI, 02903
author-two: Joseph W. Hogan
institution-two: Department of Biostatistics, School of Public Health, Brown University, 121 South Main Street, Providence, RI, 02903
  
abstract: |
  This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper.

  This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper.  This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper.
  
keywords: Machine learning, causal inference, precision optimization, bias correction, missing data.
output: 
  bookdown::pdf_document2:
    template: template.tex
    keep_tex: true
bibliography: bibliography.bib
csl: asa.csl
linkcitations: yes
colorlinks: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper.

## Subsection

This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper. This is sample text and needs to be completely replaced before submitting your paper.

### Code:

Sample code goes here!

```{r}
## sample code goes here!
2 + 2
```

### Tables:


\begin{table}
\caption{Genotypes and Their Genotypic Values for a Diallelic Locus Genotypes and Their Genotypic Values for a Diallelic Locus Genotypes and Their Genotypic Values for a Diallelic Locus Genotypes and Their Genotypic Values for a Diallelic Locus Genotypes and Their Genotypic Values for a Diallelic Locus }
\begin{center}
\begin{tabular}{ccccc}
\hline
\hline
\\[-5pt]
\multicolumn{2}{c}{Genotype} & &
\multicolumn{1}{c}{Dummy for additivity} &
\multicolumn{1}{c}{Dummy for dominance }\\
\multicolumn{1}{c}{Label} &    
\multicolumn{1}{c}{Index i} &
\multicolumn{1}{c}{Genotypic value ($\eta$)}&
\multicolumn{1}{c}{effect $\alpha$ (x)} &
\multicolumn{1}{c}{effect $\delta$ (z)}\\
\hline
qq      &1&     $\mu + \mbox{2}\alpha$  & 2&    0\\
Qq&     2&      $\mu + \alpha + \delta$&        1       &1\\
QQ&     3&      $\mu$ &  0&      0\\
\hline
\end{tabular}
\end{center}
\end{table}

### Figures:

\begin{figure}[t]
%\centering\includegraphics[scale=.75]{fig1.eps}
\caption{Place figure caption here.}
\end{figure}


This is a sample reference @lyngs2019

# REFERENCES {-}
<!--\itemsep=0pt -->

